---
title: "Mimic Electrolyte Analysis"
output: 
  html_notebook:
    toc: true  
    depth: 3
    theme: simplex
editor_options:
  chunk_output_type: inline
---

## Load Libraries
Load all relevant R libraries.
```{r Load Libaries, message=FALSE, warning=FALSE,  results='hide'}
# Load Libraries 
library("RPostgres")
library("ggplot2")
library("tidyverse")
library("dbplyr")
library("lubridate")
library("data.table")
library("dtplyr")
library("ggpubr")
library("muStat")
library("mvnormtest")
library("knitr")
library("kableExtra")
```

## Connect to Relational Database 
```{r Connect to Relational Database, message=FALSE, warning=FALSE}
# load the PostgreSQL driver
drv <- dbDriver("Postgres")

# create a connection to the postgres database
# set the search path to the mimiciii schema
con <- dbConnect(drv, dbname = "mimic",
                 host = "localhost", port = 5432,
                 user = "mousaghannam")
dbSendQuery(con, 'set search_path to mimiciii')
```

#### Show a list of all the tables in the relational database. 
```{r}
# show a list of tables
dbListTables(con)
```

#### Function for more easily pulling a given table.
This is a memory conservative approaching for performing SQL queries on DB. We can pull tables in memory and do certain analyses on them, without actually having to save a given object into the R environment. 
```{r}
#Memory conserative approaching for performing SQL queries on DB 
#(Rewrite this function to handle multiple inputs )
tbl_mimic <- function(table) {
  table <- as.character(substitute(table))
  tbl(con, dbplyr::in_schema("mimiciii", table))
}
```

### Create dictionary of diagnosis codes
This "dictionary" will contain all of the diagnoses events in the database associated with a given hospital admission id (`hadm_id`), along with a description of the icd9 code. 
```{r}
#Pull dictionary for diagnoses
d_icd_diagnoses <- tbl_mimic(d_icd_diagnoses) %>%
  select(icd9_code, short_title)

diagnoses_icd <-tbl_mimic(diagnoses_icd) %>%
  select(hadm_id, icd9_code, seq_num)

#ICD-9 Codes + their descriptions
icd9_dict <- diagnoses_icd %>%
  inner_join(d_icd_diagnoses, by = "icd9_code")

icd9_dict
```
## Load Electrolyte Lab Measurements

### Determine the ids corresponding to lab values for each electrolyte 
Saved all of the lab_ids into R environment with `collect()`, for filtering in the next step.
```{r}
d_labitems <- tbl_mimic(d_labitems) #Pull dictionary for lab items into memory 

d_labitems %>%
  filter(str_detect(tolower(label), "potassium")) %>%
  collect() -> lab_idsK

lab_idsK
```
#### Filter them 
We are choosing to include the 1st and 4th row, which are strictly blood lab value draws for potassium. 
```{r}
#Drugs to include for potassium 
itemidsK <- lab_idsK$itemid[c(1,4)]
```
### Pull table containing all lab measurements.
We are now taking the table `labevents`, which contains all the lab events in the database, and selecting the rows associated with the two blood potassium lab values `itemid`s that we chose above. 
```{r}
labevents <- tbl_mimic(labevents)

labevents %>% 
  filter(itemid %in% itemidsK)  %>%
  inner_join(select(tbl_mimic(d_labitems),-loinc_code, -row_id ), by = "itemid") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum, valueuom, label, flag, fluid, category) -> labEventsK

labEventsK %>% count() %>% collect() -> numLabKevents

labEventsK

print(paste(" There are ",pull(numLabKevents[1,1]), " total potassium lab values that were extracted from the labevents table." ))

```
## Define repletion events within the metaview database
The `d_items` table in mimics contains a dictionary for all of the events associated with both the metaview and careview database. We are only going to focus on the metaview database at this point. We then want to filter this table by the label description for items that are related to potassium. 
```{r}
d_items <- tbl_mimic(d_items) #Pull dictionary for all lab events into memory 

d_items %>%
  filter(label %ilike% "%potassium%" | label %ilike% "%kcl%") %>%
  filter(str_detect(tolower(dbsource), "meta")) %>%
  arrange(label) -> k_items_MV

k_items_MV 

```
Although there are events sourced from either metaview or careview, these two hospital databases are actually linked to 3 different tables in the mimics database: `inputevents_mv`, `inputevents_cv` or `chartevents.` Since we are examining only the metavision database, it will only link to `inputevents_mv` and `chartevents.` We would like to select for only the events that link to  `inputevents_mv`.

```{r}
k_items_MV %>% 
  filter(linksto=="inputevents_mv") %>% collect() -> k_items_MV_IM

k_items_MV_IM
```
If you look at the above table, the first row has a KCL (Bolus) with unit mL, while the 5th row has Potassium Chloride with units in mEq. According to the mimics iii website: 

> "Metavision records IO data using two tables: RANGESIGNALS and ORDERENTRY. These tables do not appear in MIMIC-III as they have been merged to form the > INPUTEVENTS_MV table. RANGESIGNALS contains recorded data elements which last for a fixed period of time. Furthermore, the RANGESIGNALS table recorded > information for each component of the drug separately. For example, for a norepinephrine administration there would be two components: a main order    > component (norepinephrine) and a solution component (NaCl)." [^1]

[^1]: <em>https://mimic.physionet.org/mimicdata/io/</em> 

Therefore, we will only be selecting repletions based off of the "main order component", and ignoring the solution. We will select for the 4th and 5th rows, which correspond to Potassiume Acetate and Potassium Chloride. 

```{r}
k_items_MV_IM %>% slice(-6,-3, -2,-1) -> k_items_MV_IM #ONLY KEEPING THE REPLETIONS, THE ADDITIVE AMOUNTS, NOT THE BOLUS 
k_items_MV_IM

k_items_MV_IM %>% pull(itemid) -> k_items_MV_IM_vector 
```
## Pull repletion events from metaview databse
We will now use the filtered ids for the two additive solutions above to pull electrolyte repletions from the `inputevents_mv` table.
```{r}
inputevents_mv <- tbl_mimic(inputevents_mv)

inputevents_mv %>%
  filter(itemid %in% k_items_MV_IM_vector) %>%
  select(subject_id, hadm_id,icustay_id, linkorderid, orderid, itemid, starttime, endtime, amount, amountuom, rate, rateuom, statusdescription, ordercomponenttypedescription) %>%
  filter(!statusdescription == "Rewritten") %>%
  rename(itemid.repletion = itemid) -> repEventsK

repEventsK
```
Determine the amount of potassium repletions: 
```{r Potassium Repletion Count}
repEventsK %>% count() %>% collect() -> numKRepletions

print(paste(" There are ",pull(numKRepletions[1,1]), " total potassium repletions that were extracted from the inputevents_mv table." ))

```

## Join tables containing repletion events and lab events 
Both the tables containing the lab draws and the repletion events have been extracted. We can now join them to begin analyzing the relationship between them. 

In addition to joining the tables, we have renamed the column corresponding to the moment the fluid collection for the lab value was recorded, `charttime`, as `charttime.lab` for clarity. 
```{r Join Repletions and Lab Events}
repEventsK %>% 
  inner_join(labEventsK, by=c("subject_id" = "subject_id", "hadm_id" = "hadm_id")) %>%
  distinct() %>%
  rename(charttime.lab = charttime) %>%
  collect() -> k_lab_repletions_MV_new

k_lab_repletions_MV_new
```
### Find recent repletions
We want to flag all repletion events that occurred either 24 hours before or 24 hours after a given lab value. We then filter the table, storing all of the repletions occurring BEFORE a given lab value in one table, and all of the ones occurring AFTER a given lab value in another. 
```{r}
#Find the RECENT Repletions
k_lab_repletions_MV_new %>%
  mutate(charttime.lab= as_datetime(charttime.lab), endtime=as_datetime(endtime), starttime = as_datetime(starttime)) %>%
  mutate(isRecentPre = difftime(starttime, charttime.lab, units = "hours") <= 24 & difftime(starttime, charttime.lab, units = "hours") > 0 ) %>%
  mutate(isRecentPost = difftime(endtime, charttime.lab, units = "hours") >= -24 & difftime(endtime, charttime.lab, units = "hours") < 0 )  -> allRepLabEvents

allRepLabEvents %>% 
  filter(isRecentPre | isRecentPost)
```

### Extract the most recent repletion, prior and after a given lab value. 
We have a table that contains all of the repletion events that occur either 24 hours prior or after a given lab value. We then group the rows by each subject and hospital id, as well as the time of fluid acquisition for the lab value. Then, we create a column that generates a flag if the lab value that is chosen is the minimum `starttime` for all the possible `starttime`s. Because there are multiple lab values, as well as multiple repletion events, for a given `hadm_id` the table outputted has all the possible permutations. We want to select the most recent repletion AFTER a lab value, so we choose the repletion with the `starttime` equal to the minimum `starttime` for a given lab value. 

```{r}
#Potassium lab event PRE-repletions 
allRepLabEvents %>%
  filter(isRecentPre) %>% 
  group_by(subject_id, hadm_id,charttime.lab) %>%
  mutate(isMostRecentRepletion = starttime == min(starttime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, starttime) %>%
  mutate(isMostRecentLabEvent = charttime.lab == max(charttime.lab)) %>%
  filter(isMostRecentLabEvent)  %>% distinct() -> pre_k_lab_repletions_MV_new

pre_k_lab_repletions_MV_new
```

For the post-repletion lab values, we are now doing the same thing, but instead finding the maximum endtime prior to a given lab value, to select the most recent repletion prior to a given lab value. 

```{r}
#Potassium lab event POST-repletions 
allRepLabEvents %>%
  filter(isRecentPost) %>% 
  group_by(subject_id, hadm_id,charttime.lab) %>%
  mutate(isMostRecentRepletion = endtime == max(endtime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, endtime) %>%
  mutate(isMostRecentLabEvent = charttime.lab == min(charttime.lab)) %>%
  filter(isMostRecentLabEvent)  %>% distinct() -> post_k_lab_repletions_MV_new

post_k_lab_repletions_MV_new
```


We then combine all of the values from the "pre-repletion" and "post-repletion" tables, into one table. We create a new column `preVsPost` to indicate if a given event is either before or after a lab value. Conceivably, the same repletion could correspond to a 

```{r}
#Combine them into one dataset 
k_pre_post_repletions_MV_new <- bind_rows(list(pre_repletion = pre_k_lab_repletions_MV_new, post_repletion = post_k_lab_repletions_MV_new), .id = "preVsPost")
k_pre_post_repletions_MV_new %>% distinct()

```

## Non Repletion Events
We will now determine the set of lab values for which there was no immediate repletion afterward. 

### Extract non-repleted values within 24 hours
In this section, we have started by filtering all the repletions prior and after a lab value, just like for the analysis on the repletions. However, this time, if there are multiple lab values that occur before a given repletion (or after), we are taking the ones after the first one. 

```{r}
#Potassium lab event PRE-repletions 
allRepLabEvents %>%
  filter(isRecentPre) %>% 
  group_by(subject_id, hadm_id,charttime.lab) %>%
  mutate(isMostRecentRepletion = starttime == min(starttime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, starttime) %>%
  mutate(isMostRecentLabEvent = charttime.lab == max(charttime.lab)) %>%
  filter(!isMostRecentLabEvent)  %>% distinct() -> nonRepletLabsPre 

#Potassium lab event POST-repletions 
allRepLabEvents %>%
  filter(isRecentPost) %>% 
  group_by(subject_id, hadm_id,charttime.lab) %>%
  mutate(isMostRecentRepletion = endtime == max(endtime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, endtime) %>%
  mutate(isMostRecentLabEvent = charttime.lab == min(charttime.lab)) %>%
  filter(!isMostRecentLabEvent)  %>% distinct() -> nonRepletLabsPost

allNonRepletions <- bind_rows(list(pre_repletion = nonRepletLabsPre, post_repletion = nonRepletLabsPost), .id = "preVsPost")
```

## Exclusions 
We now want to exclude all the rows based on certain criteria. 

We have a table called `hadm_id_table` which contains all of the hadm_ids of patients with diagnoses that would confound our results (kidney disease, etc). (WILL ADD HOW I CREATED THIS TABLE LATER).

```{r}
hadm_id_table
```

As a result, we could simply do a semi-join to determine how many people in each group were excluded. **Note**, we are doing the anti-join on the table with the most recent repletion before and after a given lab result, within a 24 hour time range. We are **not** doing it on the set of ALL possible repletion and or lab result events. 

```{r}
hadm_id_table %>%
  semi_join(k_pre_post_repletions_MV_new, by = "hadm_id") %>% 
  select(hadm_id, .id) %>%
  group_by(.id) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()
```

And here is the resultant dataset after *actually* excluding this time, using an anti-join instead. 
```{r}
k_pre_post_repletions_MV_new %>%
  anti_join(hadm_id_table, by = "hadm_id") -> postExclusionsK_Repleted

postExclusionsK_Repleted
```

## Analysis and Visualization 
We are going to do analysis here on the dataset containing repletions. We are making this distinction, as later on, we will do analysis on non-repletions. 

### Analysis on Repletions
#### Table
In this table we are just doing some summary analysis on the dataset. 

```{r}
postExclusionsK_Repleted %>%
  group_by( preVsPost) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T)) 
```

#### Histogram
Histogram of Pre and Post Repletions
```{r,fig.subcap= "Pre Vs Post Repletion Lab Values"}
ggpar(gghistogram(data = postExclusionsK_Repleted, x="valuenum", fill = "preVsPost",  add="mean", palette = c("#00AFBB", "#E7B800"),add_density = FALSE, bins = 40, gggtheme = theme_pubr(), xlab = "Lab Value", title = "Pre Vs Post Repletion Lab Values - Potassium", ylab = "Repletions")
      , xlim = c(2,6))

ggplot(postExclusionsK_Repleted, aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=40, aes(y = ..density..), color="black") + scale_x_continuous(limits = c(2,6)) + theme_pubr()

```

### Non - Repletion Analysis 

```{r}
allNonRepletions <- bind_rows(list(pre_repletion = nonRepletLabsPre, post_repletion = nonRepletLabsPost), .id = "preVsPost")

#Run Exclusions
allNonRepletions %>%
  anti_join(hadm_id_table, by = "hadm_id") -> postexclusion_nonRepletions

postexclusion_nonRepletions
```


#### Table 

```{r}
postexclusion_nonRepletions %>%
  group_by( preVsPost) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T)) 
```


### Combining the repleted vs NonRepleted pre lab values for comparison
```{r}
repletedVsNonRepleted_PreV <- bind_rows(list(repleted = postExclusionsK_Repleted, nonRepleted = postexclusion_nonRepletions), .id = "repleteVsNon") %>% filter(preVsPost == "pre_repletion")
repletedVsNonRepleted_PreV %>% distinct()
```
#### Table
```{r}
#Table
repletedVsNonRepleted_PreV %>%
  group_by(repleteVsNon,flag) %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) %>%
  mutate(percentage = observations / sum(observations) * 100) 
```


#### Visualization

```{r}
#Visualizing the non-repleted vs repleted lab values 
ggpar(gghistogram(data = repletedVsNonRepleted_PreV, x="valuenum", fill = "flag", add="mean",position = "identity", palette = c("#00AFBB", "#E7B800"),add_density = FALSE, bins = 100, gggtheme = theme_pubr(), xlab = "Lab Value", title = "Pre Vs Post Repletion Lab Values - Potassium", ylab = "Repletions", facet.by = "repleteVsNon")
      , xlim = c(2,6))
```
**Question**: How can there be histogram bars that are "abnormal" on top of bars that are white? Are they just not granular enough to differentiate them? 
I think there are errors in how the data was flagged. Should look more into this. 
#### Looking at the outliers 

##### Repleted above the threshold.
```{r}
repletedVsNonRepleted_PreV %>%
  filter(repleteVsNon == "repleted") %>%
  filter(flag == "abnormal" & valuenum > 4) %>%
  ungroup()%>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) 
```

##### Didn't replete Below the threshold.

###### Table 
```{r}
postexclusion_nonRepletions %>%
  filter(flag == "abnormal" & valuenum < 4) %>%
  ungroup() %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) 
```

###### Visualization of not repletiong below the threshold

```{r}
postexclusion_nonRepletions %>%
  filter(valuenum < 3.5 & flag == "abnormal") %>%
  ggplot(aes(x = valuenum)) +
  geom_histogram(alpha=0.6, position="identity",bins=14, color="black") + scale_x_continuous(limits = c(1,3.5)) + theme_pubr()
```
## Time of Day Analysis 
Examining the time of day for each repletion and lab value. 

```{r}
repletedVsNonRepleted_PreV %>%
  mutate(RepletionHour = hour(starttime), LabHour = hour(charttime.lab)) %>%
  gghistogram(x = c("LabHour","RepletionHour"), bins = 24, palette  = "uchicago", alpha = 0.5, merge = T, xlab = "Hours", ylab = "Number of Occurences")

repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab) + 4, RepletionHour = hour(starttime)) %>%
  pivot_longer(cols = c(LabHour,RepletionHour), values_to="Hour", names_to="WhichHour") -> yy

ordered(yy$WhichHour)
yy$WhichHour <- factor(yy$WhichHour, ordered = FALSE)
yy$WhichHour <- relevel(yy$WhichHour,"RepletionHour")
ggplot(yy, aes(x = Hour,fill=WhichHour)) + geom_histogram(position="identity",bins = 24,alpha=0.6) + 
  scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()

ggplot(yy, aes(x = Hour,fill=WhichHour)) +
  geom_histogram(alpha=0.4, position="identity",bins=24, color="black") + scale_x_continuous(breaks=seq(0,24,2)) + facet_wrap(vars(repleteVsNon))
```

#### Pre-Repletion vs Non-Repleted Lab Values 
Below, we have the time of day for lab value draws that occur for lab values that were repleted, and those that did not directly lead to a repletion. 

It seems that those leading to a repltion were more likely to occur in the morning, while those that did not directly lead to a repletion were more likely to occur in the afternoon. 

Why is this occurring? 
Perhaps, repletions in the morning are  routine, but there is no routine in performing repletions in the afternoon. 
```{r}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  ggplot(aes(x = LabHour,fill=repleteVsNon)) + geom_histogram(position="identity",bins = 24,alpha=0.6, color = "black") + scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()

```

#### Average pre-repletion lab value at each hour 
##### Table
```{r}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  pivot_wider(names_from = repleteVsNon, values_from = mean_lab_value)
```


##### Visualization

```{r message=FALSE, warning=FALSE}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  ggbarplot(x="LabHour", y = "mean_lab_value", fill = "repleteVsNon", facet.by = "repleteVsNon" ) +
  scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()

repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  ggplot(aes(x=LabHour,y=mean_lab_value,fill=repleteVsNon)) + geom_bar(stat="identity", position = "dodge", color = "black") + scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()


```


