title: "Mimic Electrolyte Analysis"
---
output:
  html_notebook:
    toc: yes
    depth: 3
    theme: simplex
  html_document:
    toc: yes
    df_print: paged
editor_options:
  chunk_output_type: inline
---

## Load Libraries
Load all relevant R libraries.
```{r Load Libaries, message=FALSE, warning=FALSE,  results='hide'}
# Load Libraries 
library("RPostgres")
library("ggplot2")
library("tidyverse")
library("dbplyr")
library("lubridate")
library("data.table")
library("dtplyr")
library("ggpubr")
library("muStat")
library("mvnormtest")
library("knitr")
library("kableExtra")
library("ggstatsplot")
```

## Connect to Relational Database 
```{r Connect to Relational Database, message=FALSE, warning=FALSE}
# load the PostgreSQL driver
drv <- dbDriver("Postgres")

# create a connection to the postgres database
# set the search path to the mimiciii schema
con <- dbConnect(drv, dbname = "mimic",
                 host = "localhost", port = 5432,
                 user = "mousaghannam")
dbSendQuery(con, 'set search_path to mimiciii')
```

#### Show a list of all the tables in the relational database. 
```{r}
# show a list of tables
dbListTables(con)
```

#### Function for more easily pulling a given table.
This is a memory conservative approaching for performing SQL queries on DB. We can pull tables in memory and do certain analyses on them, without actually having to save a given object into the R environment. 
```{r}
#Memory conserative approaching for performing SQL queries on DB 
#(Rewrite this function to handle multiple inputs )
tbl_mimic <- function(table) {
  table <- as.character(substitute(table))
  tbl(con, dbplyr::in_schema("mimiciii", table))
}
```

### Create dictionary of diagnosis codes
This "dictionary" will contain all of the diagnoses events in the database associated with a given hospital admission id (`hadm_id`), along with a description of the icd9 code. 
```{r}
#Pull dictionary for diagnoses
d_icd_diagnoses <- tbl_mimic(d_icd_diagnoses) %>%
  select(icd9_code, short_title)

diagnoses_icd <-tbl_mimic(diagnoses_icd) %>%
  select(hadm_id, icd9_code, seq_num)

#ICD-9 Codes + their descriptions
icd9_dict <- diagnoses_icd %>%
  inner_join(d_icd_diagnoses, by = "icd9_code")

icd9_dict
```
## Load Electrolyte Lab Measurements

### Determine the ids corresponding to lab values for each electrolyte 
#### Potassium 
Saved all of the lab_ids into R environment with `collect()`, for filtering in the next step.
```{r}
d_labitems <- tbl_mimic(d_labitems) #Pull dictionary for lab items into memory 

d_labitems %>%
  filter(str_detect(tolower(label), "potassium")) %>%
  collect() -> lab_idsK

lab_idsK

```

#### Magnesium
```{r}
d_labitems %>%
  filter(str_detect(tolower(label), "magnesium")) %>%
  collect() -> lab_idsMg

lab_idsMg

```

#### Calcium

```{r}
d_labitems %>%
  filter(str_detect(tolower(label), "calcium")) %>%
  collect() -> lab_idsCa

lab_idsCa

```

#### Phosphate

```{r}
d_labitems %>%
  filter(str_detect(tolower(label), "phosphate")) %>%
  collect() -> lab_idsPh

lab_idsPh

```


### Filter them 
We are choosing to include the 1st and 4th row, which are strictly blood lab value draws for potassium. Do the same for the other electrolytes. 
```{r}
#Drugs to include for potassium 
itemidsK <- lab_idsK$itemid[c(1,4)]

#Drugs to include for magnesium 
itemidsMg <- lab_idsMg$itemid[c(1)]

#Drugs to include for Calcium 
itemidsCa <- lab_idsCa$itemid[c(4)]

#Drugs to include for Phosphate
itemidsPh <- lab_idsPh$itemid[c(2)]
```


### Pull table containing all lab measurements.
We are now taking the table `labevents`, which contains all the lab events in the database, and selecting the rows associated with the two blood potassium lab values `itemid`s that we chose above. 
```{r paged.print=TRUE}
labevents <- tbl_mimic(labevents)

labevents %>% 
  filter(itemid %in% itemidsK)  %>%
  inner_join(select(tbl_mimic(d_labitems),-loinc_code, -row_id ), by = "itemid") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum, valueuom, label, flag, fluid, category) -> labEventsK

labEventsK

labevents %>% 
  filter(itemid %in% itemidsMg)  %>%
  inner_join(select(tbl_mimic(d_labitems),-loinc_code, -row_id ), by = "itemid") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum, valueuom, label, flag, fluid, category) -> labEventsMg

labEventsMg

labevents %>% 
  filter(itemid %in% itemidsCa)  %>%
  inner_join(select(tbl_mimic(d_labitems),-loinc_code, -row_id ), by = "itemid") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum, valueuom, label, flag, fluid, category) -> labEventsCa

labEventsCa

labevents %>% 
  filter(itemid %in% itemidsPh)  %>%
  inner_join(select(tbl_mimic(d_labitems),-loinc_code, -row_id ), by = "itemid") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum, valueuom, label, flag, fluid, category) -> labEventsPh

labEventsPh


# print(paste(" There are ",pull(numLabKevents[1,1]), " total potassium lab values that were extracted from the labevents table." ))

```



## Define repletion events within the metaview database
### Potassium
The `d_items` table in mimics contains a dictionary for all of the events associated with both the metaview and careview database. We are only going to focus on the metaview database at this point. We then want to filter this table by the label description for items that are related to potassium. 
```{r}
d_items <- tbl_mimic(d_items) #Pull dictionary for all lab events into memory 

d_items %>%
  filter(label %ilike% "%potassium%" | label %ilike% "%kcl%") %>%
  filter(str_detect(tolower(dbsource), "meta")) %>%
  arrange(label) -> k_items_MV

k_items_MV 

```
Although there are events sourced from either metaview or careview, these two hospital databases are actually linked to 3 different tables in the mimics database: `inputevents_mv`, `inputevents_cv` or `chartevents.` Since we are examining only the metavision database, it will only link to `inputevents_mv` and `chartevents.` We would like to select for only the events that link to  `inputevents_mv`.

```{r}
k_items_MV %>% 
  filter(linksto=="inputevents_mv") %>% collect() -> k_items_MV_IM

k_items_MV_IM
```
If you look at the above table, the first row has a KCL (Bolus) with unit mL, while the 5th row has Potassium Chloride with units in mEq. According to the mimics iii website: 

> "Metavision records IO data using two tables: RANGESIGNALS and ORDERENTRY. These tables do not appear in MIMIC-III as they have been merged to form the > INPUTEVENTS_MV table. RANGESIGNALS contains recorded data elements which last for a fixed period of time. Furthermore, the RANGESIGNALS table recorded > information for each component of the drug separately. For example, for a norepinephrine administration there would be two components: a main order    > component (norepinephrine) and a solution component (NaCl)." [^1]

[^1]: <em>https://mimic.physionet.org/mimicdata/io/</em> 

Therefore, we will only be selecting repletions based off of the "main order component", and ignoring the solution. We will select for the 4th and 5th rows, which correspond to Potassiume Acetate and Potassium Chloride. 

```{r}
k_items_MV_IM %>% slice(-6,-3, -2,-1) -> k_items_MV_IM #ONLY KEEPING THE REPLETIONS, THE ADDITIVE AMOUNTS, NOT THE BOLUS 
k_items_MV_IM

k_items_MV_IM %>% pull(itemid) -> k_items_MV_IM_vector 
```

### Magnesium
```{r}
d_items <- tbl_mimic(d_items) #Pull dictionary for all lab events into memory 

d_items %>%
  filter(label %ilike% "%magnesium%" | label %ilike% "%mg%") %>%
  filter(str_detect(tolower(dbsource), "meta")) %>%
  arrange(label) -> mg_items_MV

mg_items_MV %>% 
  filter(linksto=="inputevents_mv") %>% collect() -> mg_items_MV_IM

mg_items_MV_IM

mg_items_MV_IM %>% slice(1) -> mg_items_MV_IM #ONLY KEEPING THE REPLETIONS, THE ADDITIVE AMOUNTS, NOT THE BOLUS 
mg_items_MV_IM

mg_items_MV_IM %>% pull(itemid) -> mg_items_MV_IM_vector 

```

### Calcium
```{r}
d_items %>%
  filter(label %ilike% "%calcium%" ) %>%
  filter(str_detect(tolower(dbsource), "meta")) %>%
  arrange(label) -> ca_items_MV

ca_items_MV 

ca_items_MV %>% 
  filter(linksto=="inputevents_mv") %>% collect() -> ca_items_MV_IM

ca_items_MV_IM

ca_items_MV_IM %>% slice(1) -> ca_items_MV_IM #ONLY KEEPING THE REPLETIONS, THE ADDITIVE AMOUNTS, NOT THE BOLUS 
ca_items_MV_IM

ca_items_MV_IM %>% pull(itemid) -> ca_items_MV_IM_vector 

```

### Phosphate
```{r}
d_items %>%
  filter(label %ilike% "%phosphate%"  | label %ilike% "na%") %>%
  filter(str_detect(tolower(dbsource), "meta")) %>%
  arrange(label) -> ph_items_MV

ph_items_MV 

ph_items_MV %>% 
  filter(linksto=="inputevents_mv") %>% collect() -> ph_items_MV_IM

ph_items_MV_IM

ph_items_MV_IM %>% slice(1,8) -> ph_items_MV_IM #ONLY KEEPING THE REPLETIONS, THE ADDITIVE AMOUNTS, NOT THE BOLUS 
ph_items_MV_IM

ph_items_MV_IM %>% pull(itemid) -> ph_items_MV_IM_vector 
```

## Pull repletion events from metaview databse
### Potassium 
We will now use the filtered ids for the two additive solutions above to pull electrolyte repletions from the `inputevents_mv` table.
```{r}
inputevents_mv <- tbl_mimic(inputevents_mv)

inputevents_mv %>%
  filter(itemid %in% k_items_MV_IM_vector) %>%
  select(subject_id, hadm_id,icustay_id, linkorderid, orderid, itemid, starttime, endtime, amount, amountuom, rate, rateuom, statusdescription, ordercomponenttypedescription,cgid) %>%
  filter(!statusdescription == "Rewritten") %>%
  rename(itemid.repletion = itemid) -> repEventsK

repEventsK
```
Determine the amount of potassium repletions: 
```{r Potassium Repletion Count}
repEventsK %>% count() %>% collect() -> numKRepletions

print(paste(" There are ",pull(numKRepletions[1,1]), " total potassium repletions that were extracted from the inputevents_mv table." ))

```
### Magnesium
```{r}
inputevents_mv %>%
  filter(itemid %in% mg_items_MV_IM_vector) %>%
  select(subject_id, hadm_id,icustay_id, linkorderid, orderid, itemid, starttime, endtime, amount, amountuom, rate, rateuom, statusdescription, ordercomponenttypedescription,cgid) %>%
  filter(!statusdescription == "Rewritten") %>%
  rename(itemid.repletion = itemid) -> repEventsMg

repEventsMg
```

### Calcium
```{r}
inputevents_mv %>%
  filter(itemid %in% ca_items_MV_IM_vector) %>%
  select(subject_id, hadm_id,icustay_id, linkorderid, orderid, itemid, starttime, endtime, amount, amountuom, rate, rateuom, statusdescription, ordercomponenttypedescription,cgid) %>%
  filter(!statusdescription == "Rewritten") %>%
  rename(itemid.repletion = itemid) -> repEventsCa

repEventsCa
```

### Phosphate
```{r}
inputevents_mv %>%
  filter(itemid %in% ph_items_MV_IM_vector) %>%
  select(subject_id, hadm_id,icustay_id, linkorderid, orderid, itemid, starttime, endtime, amount, amountuom, rate, rateuom, statusdescription, ordercomponenttypedescription,cgid) %>%
  filter(!statusdescription == "Rewritten") %>%
  rename(itemid.repletion = itemid) -> repEventsPh

repEventsPh
```


## Join tables containing repletion events and lab events 
Both the tables containing the lab draws and the repletion events have been extracted. We can now join them to begin analyzing the relationship between them. 

In addition to joining the tables, we have renamed the column corresponding to the moment the fluid collection for the lab value was recorded, `charttime`, as `charttime.lab` for clarity. 
```{r Join Repletions and Lab Events}
repEventsK %>% 
  inner_join(labEventsK, by=c("subject_id" = "subject_id", "hadm_id" = "hadm_id")) %>%
  distinct() %>%
  rename(charttime.lab = charttime) %>%
  collect() -> k_lab_repletions_MV_new

k_lab_repletions_MV_new

#Magnesium
repEventsMg %>% 
  inner_join(labEventsMg, by=c("subject_id" = "subject_id", "hadm_id" = "hadm_id")) %>%
  distinct() %>%
  rename(charttime.lab = charttime) %>%
  collect() -> mg_lab_repletions_MV_new

mg_lab_repletions_MV_new

#Calcium 
repEventsCa %>% 
  inner_join(labEventsCa, by=c("subject_id" = "subject_id", "hadm_id" = "hadm_id")) %>%
  distinct() %>%
  rename(charttime.lab = charttime) %>%
  collect() -> ca_lab_repletions_MV_new

ca_lab_repletions_MV_new
#Phosphate
repEventsPh %>% 
  inner_join(labEventsPh, by=c("subject_id" = "subject_id", "hadm_id" = "hadm_id")) %>%
  distinct() %>%
  rename(charttime.lab = charttime) %>%
  collect() -> ph_lab_repletions_MV_new

ph_lab_repletions_MV_new

#Combine into one dataset
all_repletions_MV_new_AEs <- bind_rows(list( potassium = k_lab_repletions_MV_new, magnesium = mg_lab_repletions_MV_new, calcium = ca_lab_repletions_MV_new, phosphate = ph_lab_repletions_MV_new), .id = "Electrolyte")

all_repletions_MV_new_AEs
```
### Find recent repletions
We want to flag all repletion events that occurred either 24 hours before or 24 hours after a given lab value. We then filter the table, storing all of the repletions occurring BEFORE a given lab value in one table, and all of the ones occurring AFTER a given lab value in another. 
```{r}
# #Find the RECENT Repletions
all_repletions_MV_new_AEs %>%
  mutate(charttime.lab= as_datetime(charttime.lab), endtime=as_datetime(endtime), starttime = as_datetime(starttime)) %>%
  mutate(isRecentPre = difftime(starttime, charttime.lab, units = "hours") <= 24 & difftime(starttime, charttime.lab, units = "hours") > 0 ) %>%
  mutate(isRecentPost = difftime(endtime, charttime.lab, units = "hours") >= -24 & difftime(endtime, charttime.lab, units = "hours") < 0 ) -> all_electrolyte_repLabEvents

#Combine them all into one dataset 
all_electrolyte_repLabEvents <- bind_rows(list( potassium = allRepLabEvents_k, magnesium = allRepLabEvents_mg, calcium = allRepLabEvents_ca, phosphate = allRepLabEvents_ph), .id = "Electrolyte")

#Filter ones that occurred in past 24 hours 
all_electrolyte_repLabEvents %>%
  filter(isRecentPost | isRecentPre) -> all_electrolyte_repLabEvents

all_electrolyte_repLabEvents %>% #Run exclusions on all of them 
  ungroup()%>%
  anti_join(hadm_id_table, by = "hadm_id") -> postExclusionAll_new
```


## Analysis and Visualization 
We are going to do analysis here on the dataset containing repletions. We are making this distinction, as later on, we will do analysis on non-repletions. 

### Analysis on Repletions
#### Table
In this table we are just doing some summary analysis on the dataset. 

```{r}
postExclusionsK_Repleted %>%
  group_by( preVsPost) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T)) 
```


### Extract the most recent repletion, prior and after a given lab value. 
We have a table that contains all of the repletion events that occur either 24 hours prior or after a given lab value. We then group the rows by each subject and hospital id, as well as the time of fluid acquisition for the lab value. Then, we create a column that generates a flag if the lab value that is chosen is the minimum `starttime` for all the possible `starttime`s. Because there are multiple lab values, as well as multiple repletion events, for a given `hadm_id` the table outputted has all the possible permutations. We want to select the most recent repletion AFTER a lab value, so we choose the repletion with the `starttime` equal to the minimum `starttime` for a given lab value. 

```{r}
postExclusionAll_new %>% 
  filter(isRecentPre) %>% 
  group_by(subject_id, hadm_id,charttime.lab, Electrolyte) %>%
  mutate(isMostRecentRepletion = starttime == min(starttime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, starttime, Electrolyte) %>%
  mutate(isMostRecentLabEvent = charttime.lab == max(charttime.lab)) %>%
  filter(isMostRecentLabEvent)  %>% distinct() -> pre_lab_repletions_MV_NEW_allEs

pre_lab_repletions_MV_NEW_allEs
```

For the post-repletion lab values, we are now doing the same thing, but instead finding the maximum endtime prior to a given lab value, to select the most recent repletion prior to a given lab value. 

```{r}
#All Electrolyte lab event POST-repletions 
postExclusionAll_new %>%
  filter(isRecentPost) %>% 
  group_by(subject_id, hadm_id,charttime.lab,Electrolyte) %>%
  mutate(isMostRecentRepletion = endtime == max(endtime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, endtime,Electrolyte) %>%
  mutate(isMostRecentLabEvent = charttime.lab == min(charttime.lab)) %>%
  filter(isMostRecentLabEvent)  %>% distinct() -> post_lab_repletions_MV_NEW_allEs

post_lab_repletions_MV_NEW_allEs
```

We then combine all of the values from the "pre-repletion" and "post-repletion" tables, into one table. We create a new column `preVsPost` to indicate if a given event is either before or after a lab value. 

```{r}
allEs_pre_post_repletions_MV_new <- bind_rows(list(pre_repletion = pre_lab_repletions_MV_NEW_allEs, post_repletion = post_lab_repletions_MV_NEW_allEs), .id = "preVsPost")

#Just giving the amount of distinct orders in each group 
allEs_pre_post_repletions_MV_new %>%
  select(linkorderid, Electrolyte) %>%
  distinct()%>%
  group_by(Electrolyte) %>%
  summarize(n = n())
```

## Make variables factors 
```{r}
#Change the factor order later down the line for graphs
allEs_pre_post_repletions_MV_new <- allEs_pre_post_repletions_MV_new %>% mutate(preVsPost = as.factor(preVsPost), Electrolyte = as.factor(Electrolyte))

#PreVsPost
allEs_pre_post_repletions_MV_new$preVsPost <- factor(allEs_pre_post_repletions_MV_new$preVsPost, levels = rev(levels(allEs_pre_post_repletions_MV_new$preVsPost)))

#PreVsPost
pairedDataExcluded$preVsPost <- factor(pairedDataExcluded$preVsPost, levels = rev(levels(pairedDataExcluded$preVsPost)))

#Electrolyte 
allEs_pre_post_repletions_MV_new$Electrolyte <- factor(allEs_pre_post_repletions_MV_new$Electrolyte, levels = c("potassium", "magnesium", "calcium", "phosphate"))


```


#Combine all datasets into one
We're going to make one giant dataset across all of the electrolytes. 

```{r}
all_lytes_pre_post_repletions_MV_new <- bind_rows(list( potassium = k_pre_post_repletions_MV_new, magnesium = mg_pre_post_repletions_MV_new, calcium = ca_pre_post_repletions_MV_new, phosphate = ph_pre_post_repletions_MV_new), .id = "Electrolyte")

all_lytes_pre_post_repletions_MV_new %>%
  select(linkorderid, Electrolyte) %>%
  distinct()%>%
  group_by(Electrolyte) %>%
  summarize(n = n())

allEs_pre_post_repletions_MV_new %>%
   select(linkorderid, Electrolyte) %>%
  distinct()%>%
  group_by(Electrolyte) %>%
  summarize(n = n())
```
#Paired events and frequency of events 
```{r}
#Combine them into one dataset 
k_pre_post_repletions_MV_new <- bind_rows(list(pre_repletion = pre_k_lab_repletions_MV_new, post_repletion = post_k_lab_repletions_MV_new), .id = "preVsPost")
k_pre_post_repletions_MV_new %>% distinct()

#This gives the amount of repletions events with the same linkorder id. Anything over 2 might need to be exlcuded, as this should have been broken up. It reflects the inherent error in EHRs it seems like. 
k_pre_post_repletions_MV_new  %>%
  group_by(linkorderid) %>%
  summarize(observations = n()) %>%
  arrange(desc(observations)) %>%
  count(observations)

#Filters all of the rows where there is a post and a pre-repletion value (hopefully lol) 
k_pre_post_repletions_MV_new %>%
  group_by(linkorderid) %>% 
  filter(n() == 1) %>%
  ungroup()%>% 
  group_by(preVsPost) %>%
  summarize( mean = mean(valuenum, na.rm = T), obs = n(), sd = sd(valuenum, na.rm = T))

k_pre_post_repletions_MV_new %>%
  group_by(linkorderid) %>% 
  filter(n() == 2) %>%
  ungroup()%>% 
  group_by(preVsPost) %>%
  summarize( mean = mean(valuenum, na.rm = T), obs = n(), sd = sd(valuenum, na.rm = T))
  
#This gives the frequency for the amount of unique values 
k_pre_post_repletions_MV_new  %>%
  group_by(charttime.lab) %>%
  summarize(observations = n()) %>%
  arrange(desc(observations)) %>%
  count(observations)
```


### Paired data Visualization
```{r}

#Creating the data-table
allEs_pre_post_repletions_MV_new_NoOutliers %>%
  group_by(linkorderid, Electrolyte) %>% 
  filter(n() == 2) %>%
  ungroup() %>%
  group_by(linkorderid,Electrolyte, preVsPost) %>%
  filter(n()== 1) %>%
  ungroup() -> pairedDataExcluded
```


#### Table
```{r}
  
pairedDataExcluded %>%
  group_by(Electrolyte, preVsPost) %>%
  summarize( mean = mean(valuenum, na.rm = T), obs = n(), sd = sd(valuenum, na.rm = T)) 




  
```

#### Histograms
##### Raw Counts
```{r}
pairedDataExcluded %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=40, color="black") + scale_x_continuous(limits = c(0,7) ) + theme_pubr() + xlab("Potassium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Pre repletion K", "Post repletion K"))

pairedDataExcluded %>% filter(Electrolyte == "magnesium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=38, color="black") + scale_x_continuous(limits = c(0,7) ) + theme_pubr() + xlab("Magnesium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Pre repletion Mg", "Post repletion Mg")) 


pairedDataExcluded %>% filter(Electrolyte == "calcium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=75, color="black") + scale_x_continuous(limits = c(0.5,2) ) + theme_pubr() + xlab("Calcium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Pre repletion Mg", "Post repletion Ca")) 

pairedDataExcluded %>% filter(Electrolyte == "phosphate") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=51, color="black") + scale_x_continuous(limits = c(0,7) ) + theme_pubr() + xlab("Phosphate Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Pre repletion Mg", "Post repletion Ph")) 
```

##### Proportional
```{r}

#Results as a proportion of total value
pairedDataExcluded %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=50, color="black") + scale_x_continuous(limits = c(2,7) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Potassium Value") + ylab("Proportion of Occurances") + scale_fill_discrete(name = "", labels = c("Non Repletion K", " Pre repletion K"))

  #Magnesium
pairedDataExcluded %>% filter(Electrolyte == "magnesium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=38, color="black") + scale_x_continuous(limits = c(0.5,4.2) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Magnesium Value") + ylab("Proportion of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion Mg", "Pre repletion Mg")) 

  #Calcium
pairedDataExcluded %>% filter(Electrolyte == "calcium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=75, color="black") + scale_x_continuous(limits = c(0.5,2) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Calcium Value") + ylab("Proportion of Occurances") + scale_fill_discrete(name = "", labels = c("Non Repletion Ca", " Pre repletion Ca"))

  #Phosphate
pairedDataExcluded %>% filter(Electrolyte == "phosphate") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=51, color="black") + scale_x_continuous(limits = c(0,5) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Phosphate Value") + ylab("Proportion of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion Ph", "Pre repletion Ph"))   
```
#### Stacked Bar Charts 

```{r}
pairedDataExcluded %>%
  mutate(abnormal_status = case_when( Electrolyte == "potassium" & flag == "abnormal" & valuenum > 4 ~ "aboveLimit",
  Electrolyte == "potassium" & flag == "abnormal" & valuenum < 4 ~ "belowLimit", 
  Electrolyte == "magnesium" & flag == "abnormal" & valuenum > 2 ~ "aboveLimit",
  Electrolyte == "magnesium"  & flag == "abnormal" & valuenum < 2 ~ "belowLimit", 
  Electrolyte == "calcium"  & flag == "abnormal" & valuenum > 1.06 ~ "aboveLimit",
  Electrolyte == "calcium"  & flag == "abnormal" & valuenum < 1.06 ~ "belowLimit",
  Electrolyte == "phosphate"  & flag == "abnormal" & valuenum > 3 ~ "aboveLimit",
  Electrolyte == "phosphate"  & flag == "abnormal" & valuenum < 3 ~ "belowLimit", 
  T ~ "normalLimits")) -> pairedDataExcluded_abStat


pairedDataExcluded_abStat %>%
  filter(Electrolyte == "magnesium") %>%
  select(valuenum, flag) %>%
  group_by(valuenum, flag) %>% 
  summarize(obs = n())
  


pairedDataExcluded_abStat$abnormal_status <- factor(pairedDataExcluded_abStat$abnormal_status, levels = c("aboveLimit", "normalLimits", "belowLimit"))

pairedDataExcluded_abStat %>%
  group_by(Electrolyte, preVsPost, abnormal_status) %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) %>%
  arrange(Electrolyte, preVsPost) %>%
  mutate(percentage = observations / sum(observations) * 100) -> pairedDataExcluded_preVsPost_Table

pairedDataExcluded_preVsPost_Table

#2 x 2 
pairedDataExcluded_preVsPost_Table %>% 
  ggbarplot(x = "preVsPost", y="percentage",color = "black", fill = "abnormal_status",facet.by = "Electrolyte") + scale_fill_manual(values =c( "red","green","blue") ) + theme_classic()

# 1 x 4
pairedDataExcluded_preVsPost_Table %>% 
  ggbarplot(x = "preVsPost", y="percentage",color = "black", fill = "abnormal_status",facet.by = "Electrolyte", nrow= 1, ncol= 4) + scale_fill_manual(values =c( "red","green","blue")) +theme_classic() + theme(axis.text.x=element_text(angle = 90, hjust = 0)) 
```

#### Pie Charts
```{r}

pairedDataExcluded_preVsPost_Table$abnormal_status <- factor(pairedDataExcluded_preVsPost_Table$abnormal_status, levels = c( "normalLimits","belowLimit", "aboveLimit"))

#Black outline 

pairedDataExcluded_preVsPost_Table %>%
  filter(preVsPost == "pre_repletion" & Electrolyte == "potassium") %>%
ggplot(., aes("", percentage, fill = abnormal_status)) + 
  geom_bar(stat = "identity", color = "black", size = 0.5) +
  coord_polar(theta = "y") +
  scale_fill_manual(values =c( "green","blue","red"),name = " ",
                    labels = c( "3.4-5.2","Below 3.4", "Above 5.2" )
                    ) +
  theme_void() + theme(legend.position="top")  -> pie_chart_k

pairedDataExcluded_preVsPost_Table %>%
  filter(preVsPost == "pre_repletion" & Electrolyte == "magnesium") %>%
ggplot(., aes("", percentage, fill = abnormal_status)) + 
  geom_bar(stat = "identity", color = "black", size = 0.5) +
  coord_polar(theta = "y") +
  scale_fill_manual(values =c( "green","blue","red"),name = " ",
                    labels = c( "1.6-2.6","Below 1.6", "Above 2.6" )
                    ) +
  theme_void() + theme(legend.position="top")  -> pie_chart_mg

pairedDataExcluded_preVsPost_Table %>%
  filter(preVsPost == "pre_repletion" & Electrolyte == "phosphate") %>%
  ggplot(., aes("", percentage, fill = abnormal_status)) + 
  geom_bar(stat = "identity", color = "black", size = 0.5) +
  coord_polar(theta = "y") +
  scale_fill_manual(values =c( "green","blue","red"),name = " ",
                    labels = c( "2.6-X","Below 2.6", "Above 2.6" )
                    ) +
  theme_void() + theme(legend.position="top")  -> pie_chart_ph
```


## Linear regression 
```{r}
# allEs_pre_post_repletions_MV_new %>%
#   group_by(linkorderid, Electrolyte) %>%
#   filter(n() == 2) %>%
#   ungroup()%>%
#   group_by(preVsPost, Electrolyte) %>%
#   summarize( mean = mean(valuenum, na.rm = T), obs = n(), sd = sd(valuenum, na.rm = T))

pairedDataLong %>%
  group_by(Electrolyte) %>%
  summarize(pre_repletion.mean = mean(pre_repletion, na.rm=T), post_repletion.mean =  mean(post_repletion, na.rm=T))

# allEs_pre_post_repletions_MV_new %>%
#   group_by(linkorderid, Electrolyte) %>% 
#   filter(n() == 2) %>%
#   ungroup() -> pairedDataExcluded

pairedDataExcluded %>% 
  group_by(Electrolyte, preVsPost) %>%
  summarize(mean = mean(valuenum, na.rm = T)) %>%
  pivot_wider(names_from = preVsPost, values_from = c("mean")) %>%
  mutate(delta = post_repletion - pre_repletion)

#What makes some values slip through the cracks, when I am supposed to be choosing the most recent value  
pairedDataExcluded %>% 
  select(Electrolyte, preVsPost, valuenum, linkorderid) %>%
  group_by(Electrolyte,linkorderid, preVsPost) %>%
  mutate(row = row_number()) %>%
  pivot_wider(id_cols = c(linkorderid,row,Electrolyte), names_from = "preVsPost", values_from = valuenum) %>%
  select(-row) %>%
  filter(!is.na(pre_repletion) | !is.na(post_repletion)) %>%
  mutate(delta = post_repletion - pre_repletion) -> pairedDataLong

#Subset the data by Electrolyte into different dataframes 
pairedDataLong.K <- pairedDataLong %>% filter(Electrolyte == "potassium")
pairedDataLong.Mg <- pairedDataLong %>% filter(Electrolyte == "magnesium")
pairedDataLong.Ca <- pairedDataLong %>% filter(Electrolyte == "calcium")
pairedDataLong.Ph <- pairedDataLong %>% filter(Electrolyte == "phosphate")

#Generate plots for each subset of the data 
plot(delta ~ pre_repletion, data = pairedDataLong.K)
plot(delta ~ pre_repletion, data = pairedDataLong.Mg)
plot(delta ~ pre_repletion, data = pairedDataLong.Ca)
plot(delta ~ pre_repletion, data = pairedDataLong.Ph)

#Perform linear regression analysis across each electrolyte  
pairedDataLong.K.lm <- lm(delta ~ pre_repletion, data = pairedDataLong.K)
summary(pairedDataLong.K.lm)

pairedDataLong.Mg.lm <- lm(delta ~ pre_repletion, data = pairedDataLong.Mg)
summary(pairedDataLong.Mg.lm)

pairedDataLong.Ca.lm <- lm(delta ~ pre_repletion, data = pairedDataLong.Ca)
summary(pairedDataLong.Ca.lm)

pairedDataLong.Ph.lm <- lm(delta ~ pre_repletion, data = pairedDataLong.Ph)
summary(pairedDataLong.Ph.lm)

#Checking for homoscedasticity
par(mfrow=c(2,2))
plot(pairedDataLong.K.lm)
par(mfrow=c(1,1))

par(mfrow=c(2,2))
plot(pairedDataLong.Mg.lm)
par(mfrow=c(1,1))

par(mfrow=c(2,2))
plot(pairedDataLong.Ca.lm)
par(mfrow=c(1,1))

par(mfrow=c(2,2))
plot(pairedDataLong.Ph.lm)
par(mfrow=c(1,1))

#Create GG Plots
pairedDataLong.K.graph <- ggplot(pairedDataLong.K, aes(x=pre_repletion, y=delta))+
                     geom_point(fill = "white", color = "black", shape  = 1) + 
                     geom_smooth(method="lm", col="blue") + 
                     stat_regline_equation(label.x = 2.5, label.y = 5) + 
                     theme_classic() + labs(x = "Pre-repletion lab value", y = "Change in lab value") + scale_x_continuous(limits = c(2,7) )

pairedDataLong.Mg.graph <- ggplot(pairedDataLong.Mg, aes(x=pre_repletion, y=delta))+
                     geom_point(fill = "white", color = "black", shape  = 1) + 
                     geom_smooth(method="lm", col="blue") + 
                     stat_regline_equation(label.x = 1, label.y = 7) + 
                     theme_classic() + labs(x = "Pre-repletion lab value", y = "Change in lab value") 

pairedDataLong.Ca.graph <- ggplot(pairedDataLong.Ca, aes(x=pre_repletion, y=delta))+
                     geom_point(fill = "white", color = "black", shape  = 1) + 
                     geom_smooth(method="lm", col="blue") + 
                     stat_regline_equation(label.x = 0.4, label.y = 1.4) + 
                     theme_classic() + labs(x = "Pre-repletion lab value", y = "Change in lab value") + scale_y_continuous(limits = c(-2,2) )

pairedDataLong.Ph.graph <- ggplot(pairedDataLong.Ph, aes(x=pre_repletion, y=delta))+
                     geom_point(fill = "white", color = "black", shape  = 1) + 
                     geom_smooth(method="lm", col="blue") + 
                     stat_regline_equation(label.x = 1, label.y = 7) + 
                     theme_classic() + labs(x = "Pre-repletion lab value", y = "Change in lab value")
par(mfrow=c(2,2))
pairedDataLong.K.graph
pairedDataLong.Mg.graph
pairedDataLong.Ca.graph
pairedDataLong.Ph.graph
par(mfrow=c(2,2))

ggarrange(pairedDataLong.K.graph, pairedDataLong.Mg.graph, pairedDataLong.Ca.graph, pairedDataLong.Ph.graph + rremove("x.text"), 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

ggscatter(pairedDataLong,x = "pre_repletion", y="delta",facet.by = "Electrolyte" ) + xlim(0,5)
gghistogram(pairedDataLong,x = "delta",facet.by = "Electrolyte") 



###THIS RETURNS THE ROWS THAT HAVE A MISSING PRE OR POST REPLETION VALUE...VERY CURIOUS! Explore later
pairedDataExcluded %>% 
  select(Electrolyte, preVsPost, valuenum, linkorderid) %>%
  group_by(Electrolyte,linkorderid, preVsPost) %>%
  mutate(row = row_number()) %>%
  pivot_wider(id_cols = c(linkorderid,row,Electrolyte), names_from = "preVsPost", values_from = valuenum) %>%
  select(-row) %>%
  filter(is.na(pre_repletion) | is.na(post_repletion))
  

ggstatsplot::ggscatterstats(
  data = pairedDataLong.K,
  x = pre_repletion,
  y = delta,
  type = "robust", # type of test that needs to be run
  xlab = "Movie budget (in million/ US$)", # label for x axis
  ylab = "IMDB rating", # label for y axis
  title = "Movie budget and IMDB rating (action)", # title text for the plot
  caption = expression(paste(italic("Note"), ": IMDB stands for Internet Movie DataBase")),
  ggtheme = theme_pubr(), # choosing a different theme
  ggstatsplot.layer = FALSE, # turn off `ggstatsplot` theme layer
  marginal.type = "densigram", # type of marginal distribution to be displayed
  xfill = "pink", # color fill for x-axis marginal distribution
  yfill = "#009E73" # color fill for y-axis marginal distribution
)
```
#### Examining Outliers 
```{r}
pairedDataExcluded %>%
  mutate(isPotassiumOutlier= case_when((Electrolyte == "potassium" & preVsPost == "pre_repletion" & valuenum >= 5)  ~ T, T~ FALSE)) %>%
  filter(isPotassiumOutlier) -> potassiumOutliers

potassiumOutliers %>%
  distinct(subject_id) %>%
  count()

potassiumOutliers %>%
  select(subject_id, hadm_id, icustay_id, starttime, endtime) %>%
  mutate(orderInterval = interval(starttime, starttime - ddays(1))) %>%
  pull(icustay_id) -> potOuticustayid

tbl_mimic(inputevents_mv) %>%
  filter(icustay_id %in% potOuticustayid) %>%
  select(icustay_id,starttime, endtime, itemid, amount, amountuom, rate,rateuom, storetime, cgid, orderid, linkorderid, ordercategoryname,secondaryordercategoryname, ordercategorydescription ) %>%
  collect()-> full_outlier_inputevents_potassium

tbl_mimic(d_items) %>%
  filter(dbsource == "metavision" & linksto =="inputevents_mv") %>%
  filter(str_detect(tolower(label), "dextrose") | str_detect(tolower(label), "insulin") | str_detect(tolower(label), "gluconate" ) | str_detect(tolower(label), "glucose" )) %>%
  collect() -> hyperKalemiaItemOrders

hyperKalemiaItemOrders %>% pull(itemid) -> hyperKalemiaItemOrders_ids

tbl_mimic(inputevents_mv) %>%
  filter(icustay_id %in% potOuticustayid) %>% 
  filter(itemid %in% hyperKalemiaItemOrders_ids) %>%
  collect() -> hyperKalemiaOrders_Potassium_Orders

potassiumOutliers %>%
  select(subject_id, hadm_id, icustay_id, starttime, endtime) %>%
  mutate(orderInterval = interval(starttime, starttime - ddays(1))) %>%
  left_join(hyperKalemiaOrders_Potassium_Orders, by = "icustay_id") %>%
  mutate(hyperKalemiaInterval = interval(starttime.y, endtime.y)) %>%
  filter(hyperKalemiaInterval %within% orderInterval) %>%
  select(subject_id.x) %>%
  distinct() %>%
  count()
# 
# all_repletions_MV_new_AEs %>%
#   mutate(charttime.lab= as_datetime(charttime.lab), endtime=as_datetime(endtime), starttime = as_datetime(starttime)) %>%
#   mutate(isRecentPre = difftime(starttime, charttime.lab, units = "hours") <= 24 & difftime(starttime, charttime.lab, units = "hours") > 0 ) %>%
#   mutate(isRecentPost = difftime(endtime, charttime.lab, units = "hours") >= -24 & dleftifftime(endtime, charttime.lab, units = "hours") < 0 ) -> all_electrolyte_repLabEvents



```


## Exclusions 
We now want to exclude all the rows based on certain criteria. 

We have a table called `hadm_id_table` which contains all of the hadm_ids of patients with diagnoses that would confound our results (kidney disease, etc). (WILL ADD HOW I CREATED THIS TABLE LATER).

```{r}
hadm_id_table
```
### Examining amount of exclusions
####First bubble of schemtic
```{r}
## Total visits (icu_stays) before any exclusions (Pt.1 of schematic)
all_repletions_MV_new_AEs %>% 
  ungroup() %>%
  select(icustay_id) %>% 
  distinct() %>%
  count()

#The amount of distinct Icu Stays across each electrolyte 
all_repletions_MV_new_AEs %>%
  ungroup()%>%
  select(icustay_id, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

#The amount of distinct repletions across each electrolyte 
all_repletions_MV_new_AEs %>%
  ungroup()%>%
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()
```
####Second bubble of schematic: Those that have been excluded pre and post 24 hrs
```{r}
all_electrolyte_repLabEvents %>% #Amount of DISTINCT ICU visits 
  ungroup()%>%
  select(icustay_id) %>% 
  distinct() %>%
  count()

all_electrolyte_repLabEvents %>% #Amount of DISTINCT Repletion Events 
  ungroup()%>%
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

#Exclusions on visits
all_electrolyte_repLabEvents %>%
  ungroup()%>%
  inner_join(hadm_id_table, by = "hadm_id") %>%
  select(icustay_id, .id) %>%
  distinct() %>%
  group_by( .id) %>%
  summarize(obs = n())

#Amount of distinct ICU visits left
postExclusionAll_new %>%
  ungroup()%>%
  anti_join(hadm_id_table, by = "hadm_id") %>% 
  select(icustay_id) %>%
  distinct() %>%
  count()

postExclusionAll_new %>% #Amount of DISTINCT Repletion Events left 
  ungroup()%>%
  anti_join(hadm_id_table, by = "hadm_id") %>% 
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()



```




####Third bubble of schematic: Those that have been excluded pre and post 24 hrs, and also the most recent lab value before and after each repletion
```{r}
allEs_pre_post_repletions_MV_new %>% #Amount of DISTINCT ICU visits 
  ungroup()%>%
  select(icustay_id) %>% 
  distinct() %>%
  count()

allEs_pre_post_repletions_MV_new %>% #Amount of DISTINCT Repletion Events 
  ungroup()%>%
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

#Exclusions on visits
# allEs_pre_post_repletions_MV_new %>%
#   ungroup()%>%
#   inner_join(hadm_id_table, by = "hadm_id") %>% 
#   select(icustay_id, .id) %>%
#   distinct() %>%
#   group_by( .id) %>%
#   summarize(obs = n())

#Amount of distinct ICU visits left
# allEs_pre_post_repletions_MV_new %>%
#   ungroup()%>%
#   anti_join(hadm_id_table, by = "hadm_id") %>% 
#   select(icustay_id) %>%
#   distinct() %>%
#   count()

allEs_pre_post_repletions_MV_new %>% #Amount of DISTINCT Repletion Events left 
  ungroup()%>%
  anti_join(hadm_id_table, by = "hadm_id") %>% 
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()
```
#### Fourth Bubble
```{r}

#Finds the amount of values in each group with extraneous values
allEs_pre_post_repletions_MV_new %>%
  ungroup()%>%
  mutate(is_extraneous_value = case_when(
    Electrolyte == "potassium" & preVsPost == "pre_repletion" & valuenum < 2 | Electrolyte == "potassium" & preVsPost == "pre_repletion" & valuenum > 7 ~ 1, 
    Electrolyte == "magnesium" & preVsPost == "pre_repletion" & valuenum > 5 ~ 1,
    Electrolyte == "phosphate" & preVsPost == "pre_repletion" & valuenum > 5 ~ 1)) %>%
  filter(is_extraneous_value == 1) %>%
  group_by(Electrolyte) %>%
  summarize(total_ns = n())

#Filters them out 
allEs_pre_post_repletions_MV_new %>%
  ungroup()%>%
  mutate(is_extraneous_value = case_when((Electrolyte == "potassium" & preVsPost == "pre_repletion" & valuenum < 2) | (Electrolyte == "potassium" & preVsPost == "pre_repletion" & valuenum > 7) ~ T, 
    Electrolyte == "magnesium" & preVsPost == "pre_repletion" & valuenum > 5 ~ T, 
    Electrolyte == "phosphate" & preVsPost == "pre_repletion" & valuenum > 5 ~ T, 
     flag == "delta" ~ T, T ~ FALSE)) %>%
    filter(is_extraneous_value == F) -> allEs_pre_post_repletions_MV_new_NoOutliers

allEs_pre_post_repletions_MV_new_NoOutliers %>%
  ungroup %>%
  select(linkorderid, Electrolyte) %>%
  distinct() %>%
  group_by(Electrolyte) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

allEs_pre_post_repletions_MV_new %>%
  filter(linkorderid == 3229975)

```


As a result, we could simply do a semi-join to determine how many people in each group were excluded. **Note**, we are doing the anti-join on the table with the most recent repletion before and after a given lab result, within a 24 hour time range. We are **not** doing it on the set of ALL possible repletion and or lab result events. 

```{r}
hadm_id_table %>%
  semi_join(all_lytes_pre_post_repletions_MV_new, by = "hadm_id") %>% 
  select(hadm_id, .id) %>%
  group_by(.id) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

## Number of hospital visits for potassium
hadm_id_table %>%
  # semi_join(k_pre_post_repletions_MV_new, by = "hadm_id") %>%
  inner_join(k_pre_post_repletions_MV_new, by = "hadm_id") %>%
  select(hadm_id, .id) %>%
  group_by(.id) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()

k_pre_post_repletions_MV_new %>%
  ungroup()%>%
  semi_join(hadm_id_table, by = "hadm_id") %>% 
  select(icustay_id, orderid) %>%
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  kable()


```
#### Estimating GFR 
NO GFR VALUES WERE STORED IN THE MV DATABASE. 
```{r}

d_items %>%
  filter(str_detect(tolower(label), "crea")) 
#ITEMID 12698 is for creatinine in the metavision 
labevents %>%
  filter(itemid == 12698)

tbl_mimic(patients) %>%
  full_join(labevents, by = "subject_id") %>%
  filter(itemid == 12698)


```
#### Caregiver ID Analysis

```{r}
tbl_mimic(caregivers) %>% collect() -> caregivers

allEs_pre_post_repletions_MV_new_NoOutliers %>%
  select(cgid) %>% 
  inner_join(caregivers, by = "cgid") %>%
  group_by(description) %>%
  summarize(n = n())





```


And here is the resultant dataset after *actually* excluding this time, using an anti-join instead. 
```{r}
k_pre_post_repletions_MV_new %>%
  anti_join(hadm_id_table, by = "hadm_id") -> postExclusionsK_Repleted

postExclusionsK_Repleted
```

## Non Repletion Events
We will now determine the set of lab values for which there was no immediate repletion afterward. 

### Extract non-repleted values within 24 hours
In this section, we have started by filtering all the repletions prior and after a lab value, just like for the analysis on the repletions. However, this time, if there are multiple lab values that occur before a given repletion (or after), we are taking the ones after the first one. 

```{r}
#All electrolyte lab event PRE-repletions 
postExclusionAll_new %>%
  filter(isRecentPre) %>% 
  group_by(subject_id, hadm_id,charttime.lab, Electrolyte) %>%
  mutate(isMostRecentRepletion = starttime == min(starttime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, starttime, Electrolyte) %>%
  mutate(isMostRecentLabEvent = charttime.lab == max(charttime.lab)) %>%
  filter(!isMostRecentLabEvent)  %>% distinct() -> nonRepletLabsPre_allEs

#All electrolyte lab event POST-repletions 
postExclusionAll_new %>%
  filter(isRecentPost) %>% 
  group_by(subject_id, hadm_id,charttime.lab, Electrolyte) %>%
  mutate(isMostRecentRepletion = endtime == max(endtime)) %>%
  filter(isMostRecentRepletion) %>%
  ungroup() %>% 
  group_by(subject_id, hadm_id, endtime, Electrolyte) %>%
  mutate(isMostRecentLabEvent = charttime.lab == min(charttime.lab)) %>%
  filter(!isMostRecentLabEvent)  %>% distinct() -> nonRepletLabsPost_allEs

allNonRepletions_allEs <- bind_rows(list(pre_repletion = nonRepletLabsPre_allEs, post_repletion = nonRepletLabsPost_allEs), .id = "preVsPost")

```
#### Table
```{r}
allNonRepletions_allEs %>%
  group_by(preVsPost, Electrolyte) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T))
```

## Analysis and Visualization 
We are going to do analysis here on the dataset containing repletions. We are making this distinction, as later on, we will do analysis on non-repletions. 

### Analysis on Repletions
#### Table
In this table we are just doing some summary analysis on the dataset. 

```{r}
allEs_pre_post_repletions_MV_new %>%
  group_by( preVsPost, Electrolyte) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T)) 

```

#### Box plot

```{r}
allEs_pre_post_repletions_MV_new_NoOutliers %>%
ggplot(., aes(x=Electrolyte, y=valuenum, fill=preVsPost)) + geom_boxplot() + theme_pubr() + scale_y_continuous(limits = c(0,10)) + scale_fill_discrete(name = "Electrolyte Value", labels = c("Pre-Repletion", "Post-Repletion")) + scale_x_discrete(labels =  c("Potassium", "Magnesium", "Calcium", "Phosphate")) + ylab("Average Value")

```


#### Histogram
Histogram of Pre and Post Repletions
```{r,fig.subcap= "Pre Vs Post Repletion Lab Values"}
ggpar(gghistogram(data = postExclusionsK_Repleted, x="valuenum", fill = "preVsPost",  add="mean", palette = c("#F8766D", "#00BFC4"),add_density = FALSE, bins = 85, gggtheme = theme_pubr(), xlab = "Lab Value", title = "Pre Vs Post Repletion Lab Values - Potassium", ylab = "Repletions")
      , xlim = c(2,6)) 

allEs_pre_post_repletions_MV_new_NoOutliers %>% filter(Electrolyte == "potassium") %>% group_by(preVsPost) %>% summarize(mean = mean(valuenum, na.rm = T)) -> mean

allEs_pre_post_repletions_MV_new_NoOutliers %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=40, color="black") + scale_x_continuous(limits = c(2,6) ) + theme_pubr() + xlab("Potassium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Post repletion K", "Pre repletion K"))  -> h1_k

h1_k + geom_vline(xintercept = mean$mean[2], linetype="dotted", color = "blue", size=1.5)

#Attempt at faceting 
ggplot(allEs_pre_post_repletions_MV_new_NoOutliers, aes(x = valuenum,fill=preVsPost)) +
  geom_histogram(alpha=0.6, position="identity",bins=40, color="black") + theme_pubr() + xlab("Potassium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Post repletion K", "Pre repletion K")) + facet_wrap( ~ Electrolyte,scales = "free", nrow = 1, ncol = 4) 

```

#### Pie Chart 

```{r}

  postExclusionsK_Repleted %>%
     mutate(repletionRange = case_when(valuenum < 3.5 & flag == "abnormal" ~ "below normal",
                                      valuenum > 3.5 & flag == "abnormal" ~ "above range",TRUE ~ "within range")) -> postExclusionsK_Repleted

postExclusionsK_Repleted %>%
  filter(repletionRange == "above range") %>% 
  group_by(valuenum) %>%
  summarize(observations = n()) %>% 
   arrange(valuenum) 


postExclusion_freq <- postExclusionsK_Repleted %>%
  group_by(repletionRange) %>%
  summarize(observations = n()) %>%
  mutate(percentage = observations / sum(observations) * 100) 


postExclusion_freq$repletionRange <- factor(postExclusion_freq$repletionRange, levels = c( "within range","below normal", "above range"))

#Black outline 
ggplot(postExclusion_freq, aes("", percentage, fill = repletionRange)) + 
  geom_bar(stat = "identity", color = "black", size = 0.5) +
  coord_polar(theta = "y") +
  scale_fill_manual(values =c( "red","blue","green"),name = " ",
                    labels = c( "Above 5.2","Below 3.4", "3.4-5.2" )
                    ) +
  theme_void() + theme(legend.position="top")  -> pie_chart_k

pie_chart_k
#White outline
ggplot(postExclusion_freq, aes("", percentage, fill = repletionRange)) + 
  geom_bar(stat = "identity", color = "white", size = 1) +
  coord_polar(theta = "y") +
  scale_fill_manual(values =c( "green","blue","red"),name = " ",
                    labels = c( "3.4-5.2","Below 3.4", "Above 5.2" )
                    ) +
  theme_void() + theme(legend.position="top") -> pie_chart_k

pie(x = postExclusion_freq$percentage)
pie_chart_k

```



### Non - Repletion Analysis 

```{r}
allNonRepletions <- bind_rows(list(pre_repletion = nonRepletLabsPre, post_repletion = nonRepletLabsPost), .id = "preVsPost")

#Run Exclusions
allNonRepletions %>%
  anti_join(hadm_id_table, by = "hadm_id") -> postexclusion_nonRepletions

postexclusion_nonRepletions
```


#### Table 

```{r}
postexclusion_nonRepletions %>%
  group_by( preVsPost) %>%
  summarize(n = n(), mean = mean(valuenum, na.rm = TRUE), standard_deviation = sd(valuenum, na.rm = T)) 
```


### Combining the repleted vs NonRepleted pre lab values for comparison
```{r}
repletedVsNonRepleted_PreV <- bind_rows(list(repleted = pairedDataExcluded, nonRepleted = allNonRepletions_allEs), .id = "repleteVsNon") %>% filter(preVsPost == "pre_repletion")

repletedVsNonRepleted_PreV %>% distinct()

repletedVsNonRepleted_PreV$Electrolyte <-  factor(repletedVsNonRepleted_PreV$Electrolyte, levels = c("potassium", "magnesium", "calcium", "phosphate"))
```
#### Table
```{r}
#Table
repletedVsNonRepleted_PreV %>%
  group_by(Electrolyte,repleteVsNon,flag) %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) %>%
  ungroup(flag) %>%
  mutate(percentage = observations / sum(observations) * 100) %>%
  arrange(Electrolyte)


```


#### Visualization

```{r}
#Visualizing the non-repleted vs repleted lab values 
ggpar(gghistogram(data = repletedVsNonRepleted_PreV, x="valuenum", fill = "flag", add="mean",position = "identity", palette = c("#00AFBB", "#E7B800"),add_density = FALSE, bins = 100, gggtheme = theme_pubr(), xlab = "Lab Value", title = "Pre Vs Post Repletion Lab Values - Potassium", ylab = "Repletions", facet.by = "repleteVsNon")
      , xlim = c(2,6))


#Raw histgram counts
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(alpha=0.6, position="identity",bins=40, color="black") + scale_x_continuous(limits = c(2,6) ) + theme_pubr() + xlab("Potassium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion K", " Pre repletion K"))

repletedVsNonRepleted_PreV %>% filter(Electrolyte == "magnesium") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(alpha=0.6, position="identity",bins=38, color="black") + scale_x_continuous(limits = c(0.5,4.2) ) + theme_pubr() + xlab("Magnesium Value") + ylab("Number of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion Mg", "Pre repletion Mg")) 




#Divided counts in each histogram by group, so histograms would have similar heights 
  #Potassium
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=50, color="black") + scale_x_continuous(limits = c(2,7) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Potassium Value") + ylab("Proportion of Occurances") + scale_fill_discrete(name = "", labels = c("Non Repletion K", " Pre repletion K"))
  #Magnesium
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "magnesium") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=38, color="black") + scale_x_continuous(limits = c(0.5,4.2) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Magnesium Value") + ylab("Proportion of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion Mg", "Pre repletion Mg")) 
  #Calcium
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "calcium") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=75, color="black") + scale_x_continuous(limits = c(0.5,2) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Calcium Value") + ylab("Proportion of Occurances") + scale_fill_discrete(name = "", labels = c("Non Repletion Ca", " Pre repletion Ca"))
  #Phosphate
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "phosphate") %>%
ggplot(., aes(x = valuenum,fill=repleteVsNon)) +
  geom_histogram(aes(y=stat(density*width)),alpha=0.6, position="identity",bins=51, color="black") + scale_x_continuous(limits = c(0,5) ) + scale_y_continuous(limits = c(0,0.25) ) + theme_pubr() + xlab("Phosphate Value") + ylab("Proportion of Occurrences") + scale_fill_discrete(name = "", labels = c("Non Repletion Ph", "Pre repletion Ph")) 
 

#Cleaner histograms showing extreme values 
repletedVsNonRepleted_PreV %>% filter(Electrolyte == "magnesium") %>%
ggplot(., aes(x = valuenum,fill=flag)) +
  geom_histogram(alpha=0.6, position="identity",bins=38, color="black") + scale_x_continuous(limits = c(0.5,4.2) ) + theme_pubr() + xlab("Magnesium Value") + ylab("Number of Occurrences") + facet_wrap(~ repleteVsNon ) + scale_fill_discrete(name = "", labels = c("Outside Reference Range", " Inside Reference Range"))

repletedVsNonRepleted_PreV %>% filter(Electrolyte == "potassium") %>%
ggplot(., aes(x = valuenum,fill=flag)) +
  geom_histogram(alpha=0.6, position="identity",bins=51, color="black") +scale_x_continuous(limits = c(1,6.5) ) + theme_pubr() + xlab("Potassium Value") + ylab("Number of Occurrences") + facet_wrap(~ repleteVsNon, ) +  scale_fill_discrete(name = "", labels = c("Outside Reference Range", " Inside Reference Range"))

repletedVsNonRepleted_PreV %>% filter(Electrolyte == "calcium") %>%
ggplot(., aes(x = valuenum,fill=flag)) +
  geom_histogram(alpha=0.6, position="identity",bins=51, color="black") +scale_x_continuous(limits = c(0,1.5) ) + theme_pubr() + xlab("Calcium Value") + ylab("Number of Occurrences") + facet_wrap(~ repleteVsNon, ) +  scale_fill_discrete(name = "", labels = c("Outside Reference Range", " Inside Reference Range"))

repletedVsNonRepleted_PreV %>% filter(Electrolyte == "phosphate") %>%
ggplot(., aes(x = valuenum,fill=flag)) +
  geom_histogram(alpha=0.6, position="identity",bins=51, color="black") +scale_x_continuous(limits = c(0,5) ) + theme_pubr() + xlab("Phosphate Value") + ylab("Number of Occurrences") + facet_wrap(~ repleteVsNon, ) +  scale_fill_discrete(name = "", labels = c("Outside Reference Range", " Inside Reference Range"))
```
**Question**: How can there be histogram bars that are "abnormal" on top of bars that are white? Are they just not granular enough to differentiate them? 
I think there are errors in how the data was flagged. Should look more into this. 
#### Looking at the outliers 

##### Repleted above the threshold.
```{r}
repletedVsNonRepleted_PreV %>%
  filter(repleteVsNon == "repleted") %>%
  filter(flag == "abnormal" & valuenum > 4) %>%
  ungroup()%>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) 
```

##### Didn't replete Below the threshold.

###### Table 
```{r}
postexclusion_nonRepletions %>%
  filter(flag == "abnormal" & valuenum < 4) %>%
  ungroup() %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) 
```

###### Visualization of not repletiong below the threshold

```{r}
postexclusion_nonRepletions %>%
  filter(valuenum < 3.5 & flag == "abnormal") %>%
  ggplot(aes(x = valuenum)) +
  geom_histogram(alpha=0.6, position="identity",bins=14, color="black") + scale_x_continuous(limits = c(1,3.5)) + theme_pubr()
```

### General Analysis on repletion vs non-repletions 
```{r}

repletedVsNonRepleted_PreV %>%
  mutate(abnormal_status = case_when( Electrolyte == "potassium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum > 4 ~ "aboveLimit",
  Electrolyte == "potassium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum < 4 ~ "belowLimit", 
  Electrolyte == "magnesium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum > 2 ~ "aboveLimit",
  Electrolyte == "magnesium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum < 2 ~ "belowLimit", 
  Electrolyte == "calcium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum > 1.06 ~ "aboveLimit",
  Electrolyte == "calcium" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum < 1.06 ~ "belowLimit",
  Electrolyte == "phosphate" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum > 3 ~ "aboveLimit",
  Electrolyte == "phosphate" & repleteVsNon == "repleted" & flag == "abnormal" & valuenum < 3 ~ "belowLimit",
  Electrolyte == "potassium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum > 4 ~ "aboveLimit",
  Electrolyte == "potassium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum < 4 ~ "belowLimit", 
  Electrolyte == "magnesium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum > 2 ~ "aboveLimit",
  Electrolyte == "magnesium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum < 2 ~ "belowLimit", 
  Electrolyte == "calcium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum > 1.3 ~ "aboveLimit",
  Electrolyte == "calcium" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum < 1.3 ~ "belowLimit",
  Electrolyte == "phosphate" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum > 3 ~ "aboveLimit",
  Electrolyte == "phosphate" & repleteVsNon == "nonRepleted" & flag == "abnormal" & valuenum < 3 ~ "belowLimit", T ~ "normalLimits")) -> repletedVsNonRepleted_PreV_abStat

repletedVsNonRepleted_PreV_abStat$abnormal_status <- factor(repletedVsNonRepleted_PreV_abStat$abnormal_status, levels = c("aboveLimit", "normalLimits", "belowLimit"))

repletedVsNonRepleted_PreV_abStat %>%
  group_by(Electrolyte, repleteVsNon, abnormal_status) %>%
  summarize(observations = n(),mean = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm=T)) %>%
  arrange(Electrolyte, repleteVsNon) %>%
  mutate(percentage = observations / sum(observations) * 100) -> repleteVsNonRepleteTable

repleteVsNonRepleteTable



repleteVsNonRepleteTable %>% 
  ggbarplot(x = "repleteVsNon", y="percentage",color = "black", fill = "abnormal_status",facet.by = "Electrolyte", nrow= 1, ncol=4) + scale_fill_manual(values =c( "red","green","blue") ) + theme_classic() + theme(axis.text.x=element_text(angle = 90, hjust = 0)) 

  
```


###Amount of people that replete (vs Non-Replete) across lab value 

```{r}
repletedVsNonRepleted_PreV %>%
  group_by(valuenum, repleteVsNon) %>%
  summarize(observations = n() ) %>%
  ggplot(aes(fill=repleteVsNon, y=observations, x=valuenum)) + 
    geom_bar(position="fill", stat="identity") + scale_x_continuous()  + theme_pubr()
```

## Time of Day Analysis 
Examining the time of day for each repletion and lab value. 

```{r}
repletedVsNonRepleted_PreV %>%
  mutate(RepletionHour = hour(starttime), LabHour = hour(charttime.lab)) %>%
  gghistogram(x = c("LabHour","RepletionHour"), bins = 24, palette  = "uchicago", alpha = 0.5, merge = T, xlab = "Hours", ylab = "Number of Occurences")

repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab) + 4, RepletionHour = hour(starttime)) %>%
  pivot_longer(cols = c(LabHour,RepletionHour), values_to="Hour", names_to="WhichHour") -> yy

ordered(yy$WhichHour)
yy$WhichHour <- factor(yy$WhichHour, ordered = FALSE)
yy$WhichHour <- relevel(yy$WhichHour,"RepletionHour")
ggplot(yy, aes(x = Hour,fill=WhichHour)) + geom_histogram(position="identity",bins = 24,alpha=0.6) + 
  scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()

ggplot(yy, aes(x = Hour,fill=WhichHour)) +
  geom_histogram(alpha=0.4, position="identity",bins=24, color="black") + scale_x_continuous(breaks=seq(0,24,2)) + facet_wrap(vars(repleteVsNon))
```

#### Pre-Repletion vs Non-Repleted Lab Values 
Below, we have the time of day for lab value draws that occur for lab values that were repleted, and those that did not directly lead to a repletion. 

It seems that those leading to a repltion were more likely to occur in the morning, while those that did not directly lead to a repletion were more likely to occur in the afternoon. 

Why is this occurring? 
Perhaps, repletions in the morning are  routine, but there is no routine in performing repletions in the afternoon. 
```{r}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  ggplot(aes(x = LabHour,fill=repleteVsNon)) + geom_histogram(position="identity",bins = 24,alpha=0.6, color = "black") + scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr() + xlab("Hour of Day") + ylab("Number of Lab Values") + scale_fill_discrete(name = "", labels = c("Non-Repletion", "Repletion"))


```

#### Average pre-repletion lab value at each hour 
##### Table
```{r}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  pivot_wider(names_from = repleteVsNon, values_from = mean_lab_value)
```


##### Visualization

```{r message=FALSE, warning=FALSE}
repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  ggbarplot(x="LabHour", y = "mean_lab_value", fill = "repleteVsNon", facet.by = "repleteVsNon" ) +
  scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()

repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T), std_dev = sd(valuenum, na.rm = T)) %>%
  ggplot(aes(x=LabHour,y=mean_lab_value,group=repleteVsNon, color = repleteVsNon)) + geom_line() + geom_point() + scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr() + geom_errorbar(aes(ymin=mean_lab_value-std_dev, ymax=mean_lab_value+std_dev), width=.2,
                 position=position_dodge(0.05))


repletedVsNonRepleted_PreV %>%
  ungroup() %>%
  mutate(LabHour = hour(charttime.lab)) %>%
  filter(preVsPost == "pre_repletion") %>%
  group_by(LabHour, repleteVsNon) %>%
  summarize(mean_lab_value = mean(valuenum, na.rm = T)) %>%
  ggplot(aes(x=LabHour,y=mean_lab_value,fill=repleteVsNon)) + geom_bar(stat="identity", position = "dodge", color = "black") + scale_x_continuous(breaks=seq(0,24,2))  + theme_pubr()
```

### Kidney Analysis 

```{r}
#Outline Codes For Each Group
kidney_failure_codes <- c("584.5","584.6","584.7","584.8","584.9")
CKD_S1_codes <- "585.1"
CKD_S2_codes <- "585.2"
CKD_S3_codes <- "585.3"
CKD_S4_codes <- "585.4"
CKD_S5_codes <- "585.5"
CKD_ESRD_codes <- "585.6"

#Put all the kidney codes in a list 
all_kidney_codes <- list(kid_failure = kidney_failure_codes, 
     CKD_S1 = CKD_S1_codes,
     CKD_S2 = CKD_S2_codes,
     CKD_S3 = CKD_S3_codes,
     CDK_S4 = CKD_S4_codes,
     CKD_S5 = CKD_S5_codes,
     CKD_ESRD = CKD_ESRD_codes)

plyr::ldply(all_kidney_codes, data.frame) -> test 
pull(test,var = "X..i.." )
icd9_dict %>% collect() %>%
  filter(icd9_code %in% test$X..i.. ) -> myCodes

icd9_codes_table_filteredICD9%>% 
  filter(code %in%pull(test,var = "X..i.." ))

#Pull the hadm_ids for each group
all_kidney_hadm_ids <- lapply(all_kidney_codes, get_hadm_IDs)
all_kidney_hadm_ids <- lapply(all_kidney_hadm_ids, collect)

#Flag the electrolyte repletions within each subgroup  
all_electrolyte_repLabEvents %>%
  mutate(is_kid_failure = hadm_id %in% all_kidney_hadm_ids$kid_failure,
         is_CKD_S1 = hadm_id %in% all_kidney_hadm_ids$CKD_S1,
         is_CKD_S2 = hadm_id %in% all_kidney_hadm_ids$CKD_S2,
         is_CKD_S3 = hadm_id %in% all_kidney_hadm_ids$CKD_S3, 
         is_CKD_S4 = hadm_id %in% all_kidney_hadm_ids$CDK_S4,
         is_CKD_S5 = hadm_id %in% all_kidney_hadm_ids$CKD_S5,
         is_CKD_S6 = hadm_id %in% all_kidney_hadm_ids$CKD_ESRD) -> all_electrolyte_repLabEventsKidneyFailureFlagged

all_electrolyte_repLabEvents %>% 
  


```


#  Citations

```{r}
citation(package = "RPostgres") 
citation(package = "dbplyr") 
citation(package = "tidyverse") 
citation(package = "ggplot2") 
citation(package = "rstatix") 
```

